Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-02 draft.tex
small discussion stuff
finished with first draft of section 3 (main proof)

Our approach here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
In particular, thanks to Knudsen \cite{Knudsen}, 
we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $E_n$ algebras, notably centralizers.

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $E_n$ algebras
\[
f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $E_n$ algebras.
The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
\end{thm}

@@

Our proof involves explicit manipulations with cochain complexes and the poset of opens in~$\RR^n$.
To connect that setting with the abstract $\infty$-categorical setting above,
we leverage deep, prior work:
\begin{itemize}
\item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
In fact, he simplifies the situation a bit more. 
Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball. 
One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
\item In particular, in addition to the factorization algebra model, Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict $\Disk_n$-algebra $\cliels(\fg[-n])$ that is strictly locally constant.
\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
In \S2 we review these results in more detail with an emphasis on what we need for our central theorem.

Here is an outline of our proof:
\begin{enumerate}
\item From the map $f: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$, 
we produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \UU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~$f$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to Z_f
\]
as factorization algebras. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Lurie-Francis result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $E_n$ algebras.

@@

In fact, Knudsen shows a stronger version of the second part.
if one restricts to working with open balls in $\RR^n$ (rather than arbitrary open sets)
then there is a $\Disk_n$-algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n])$ to each ball and it is manifestly locally constant.
This algebra ${\tt U}_n \fg$ is a model for~$\UU_n \fg$.

@@

Recall the overall strategy.
First, we define a factorization algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
Then we get to the heart of the construction:
we show that this convolution algebra naturally sits inside a centralizer diagram.
By the universal property of the centralizer, we then obtain 
a canonical map 
\[
\theta_{\bf{f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
\]
where ${\frak Z}(\mathbf{f})$ is a factorization algebra that models the centralizer ${\frak Z}(f)$ of the map $f$.
\owen{Calibrate notations!}
It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
using the Francis-Lurie result mentioned earlier.

\owen{Comment on notations:}
As we work in the setting of factorization algebras on $\RR^n$, 
we will use bold font to indicate such factorization models for $E_n$ algebra statements.
For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $E_n$ algebra,
and we use $\bf{f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $E_n$ algebras.

@@

\owen{I want to recall briefly how an $L_\infty$ action on a cochain complex leads to all the variants of CE (co)chains.
It can just be a compendium of facts we use below.}

To any $\fg$-module $M$ (whether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
we can associate its Chevalley-Eilenberg cochain complex defined 
by 
\begin{equation}
 \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
\end{equation}
with its classical differential. 
\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
We have the evaluation map 
\begin{equation}
 \label{eq:defev} \ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
\end{equation}
given by applying a function on a given tensor in $Sym(\fg[-1])$.

\begin{dfn}
\label{dfn: CE from map}
\owen{an $L_\infty$ map $\fg \rightsquigarrow \fh$ induces a cochain complex $\clies(\fg,\cliels(\fh))$.}
\end{dfn}

@@

\owen{Add a remark on convolution?}
%
%\def\conv{{\rm Conv}}
%
%\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
%
%\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^! \to A$ from $C^! = \conv(C,1)$, the ``Koszul dual'' $\cO$-algebra to the coalgebra $C$. This cocycle can be used to twist the differential of $\conv(C,A)$. Hopefully this admits an obvious deformation-theoretic interpretation.}
%
%\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}

@@

Our goal in this subsection is to construct a map of factorization algebras
\[
\ev_{\bf{f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
\]
while in the next subsection we will show it fits into a centralizer diagram.
To produce our map, we first construct it separately on each open subset and then explain why the construction is functorial.

Let $V \subset \RR^n$ be open.
The canonical pairing between Lie algebra chains and cochains provides a canonical cochain map
\[
\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \cliels(\Omega^*(V) \otimes \fg) \to \cliels(\Omega^*_c(V) \otimes \fh)_f.
\]
The canonical inclusion $\Omega^*_c(V) \otimes \fg \hookrightarrow \Omega^*(V) \otimes \fg$ induces a canonical inclusion 
\[
\cliels(\Omega^*_c(V) \otimes \fg) \hookrightarrow \cliels(\Omega^*(V) \otimes \fg)
\]
and hence, precomposing this inclusion with the pairing, we obtain our desired map
\[
\ev_{\bf{f}}(V): \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
\]
for each open~$V$.

@@

\begin{lmm}
The assignment
\[
V \mapsto \ev_{\bf{f}}(V)
\]
determines a natural transformation between functors from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
\end{lmm}

@@

\greg{
We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.\\
First note that compactly supported form embeds in all forms, therefore we can apply 
any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
  \\
 (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
\end{equation} induced by this embedding  in all forms followed by evaluating on a function.\\
Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
B(\emptyset) \ar[r] & B(U)  } 
 \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
 $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
 of the factorization structure of 
 the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
 The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
 \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
 $B$. We therefore obtain a canonical splitting of factorization algebras 
 \begin{equation}\label{eq:splittingbyaugm}
   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
 \end{equation}
given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
a natural grading on it.\\
We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
\begin{multline}\label{eq:defevforconnected}
 \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
 \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
 \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
 \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
 \right) \\
 \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
 B(W)
\end{multline}
where $\mathbf{f}$ is the factorization algebra morphism  we are given.
In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
we have 
\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
We extend this construction  to any 
 open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
 More precisely, 
  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
of its connected components. Using, the natural isomorphisms of complexes 
\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
$\bigotimes_{i\in I} B(U_i) 
\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
 (natural) decomposition 
\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
 \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
 \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
 \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
 \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
\end{multline}
and we can therefore define 
\begin{multline}\label{eq:defineevf}
 \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
 \\ \stackrel{\simeq}\longrightarrow  
\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
 \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
 \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
 \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
\end{multline}
where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
and~\eqref{eq:defevforconnected}.
\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
things to do (like completion) for non-finitely dimensional Lie algebras}
\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}\\
\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of

>>>>

Our approach here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
In particular, thanks to Knudsen \cite{Knudsen}, 
we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $E_n$ algebras, notably centralizers.

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $E_n$ algebras
\[
\UU_n f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $E_n$ algebras.
The centralizer of this map ${\frak Z}_{E_n}(\UU_n f)$ is an $E_n$-algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
\end{thm}

@@

Our proof involves explicit manipulations with cochain complexes and the poset of opens in~$\RR^n$.
To connect that setting with the abstract $\infty$-categorical setting above,
we leverage deep, prior work:
\begin{itemize}
\item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
In fact, he simplifies the situation a bit more. 
Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball. 
One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
\item Knudsen verifies that we can model the enveloping $E_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
In \S2 we review these results in more detail with an emphasis on what we need for our central theorem.

Here is an outline of our proof:
\begin{enumerate}
\item Let ${\bf f}: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~${\bf f}$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to \bZ({\bf f})
\]
as factorization algebras. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Lurie-Francis result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $E_n$ algebras.

@@

\owen{Add discussion of how this makes sense even on unoriented manifolds.}

In fact, Knudsen shows a stronger version of the second part.
if one restricts to working with open balls in $\RR^n$ (rather than arbitrary open sets)
then there is a $\Disk_n$-algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n]) = \Sym(\fg[1-n])$ to each ball and it is manifestly locally constant.
This algebra ${\tt U}_n \fg$ is a model for~$\UU_n \fg$.

@@

Recall the overall strategy.
First, we define a factorization algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
Then we get to the heart of the construction:
we show that this convolution algebra naturally sits inside a centralizer diagram.
By the universal property of the centralizer, we then obtain 
a canonical map 
\[
\theta_{{\bf f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  \bZ(\mathbf{f})
\]
where $\bZ(\mathbf{f})$ is some locally constant factorization algebra that models the centralizer ${\frak Z}(f)$ of the map $f$.
It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
using the Francis-Lurie result mentioned earlier.

\owen{Comment on notations:}
As we work in the setting of factorization algebras on $\RR^n$, 
we will use bold font to indicate such factorization models for $E_n$ algebra statements.
For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $E_n$ algebra,
and we use ${\bf f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $E_n$ algebras.

@@

\owen{Please read and comment if it is too fast or cryptic (or wrong due, e.g., to sloppy shifts).}

We assume the reader is familiar with Lie algebras and $L_\infty$ algebras and with standard constructions,
such as the Chevalley-Eilenberg chains or cochains, which we may also call the Lie algebra (co)chains.
A nice reference is \owen{Loday-Vallette???}
Nonetheless, we review a few aspects that play a crucial role below.

First, recall that an $L_\infty$ algebra $\fg$, with its collection of brackets $\{\ell_n\}_{n \geq 1}$ is fully encoded by its dg conilpotent cocommutative coalgebra
\[
\cliels(\fg) = (\Sym(\fg[1]), \d = \sum_n \ell_n)
\]
where the sum of the brackets provides a square-zero coderivation.
The square-zero condition efficiently encodes the higher Jacobi relations.
This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
Let $\overline{\cliels(\fg)} \subset \cliels(\fg)$ denote the subcoalgebra given by the direct sum over positive symmetric powers of $\fg[1]$,
which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.

By definition, an $L_\infty$ map $f: \fg \rightsquigarrow \fh$ is a (strict) map of such dg cocommutative coalgebras
\[
f: \cliels(\fg) \to \cliels(\fh).
\]
The requirement that $f$ preserves all that structure encodes efficiently that the brackets intertwine in the correct fashion.
It is then immediate that the hom-complex
\[
\Hom^\bullet (\cliels(\fg), \cliels(\fh))
\]
admits a deformed differential
\[
\d_\Hom + [f,-]
\]
known as a twisting cocycle.
We use 
\[
\clies(\fg,\cliels(\fh)_f)
\]
to denote this cochain complex whose differential depends on the choice of $L_\infty$ map~$f$,
and we call it the {\em Lie algebra cochains of $\fg$ with values in $\fh$ arising from the map~$f$}.

This complex $\clies(\fg,\cliels(\fh)_f)$ encodes the deformation theory for $L_\infty$ maps around the map $f$.
That is, in a sufficiently sophisticated geometric setting, it is the tangent complex to the mapping space of $L_\infty$ maps from $\fg$ to~$\fh$.
One should view $f$ as the basepoint for this tangent complex.
Due to the splitting
\[
\cliels(\fg) = k \oplus \overline{\cliels(\fg)},
\]
we have a decomposition
\[
\clies(\fg,\cliels(\fh)_f) \cong \cliels(\fh) \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f),
\]
which plays a crucial role in our argument.

Indeed, consider the canonical evaluation pairing
\[
\ev_{f}: \clies(\fg,\cliels(\fh)_f) \otimes \cliels(\fg) \to \cliels(\fh)
\]
sending $(1 + g, x)$ to $f(x) + g(x)$, where $g \in \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)$.
In this sense, we see how the Lie algebra cochains arising from $f$ encodes deformations.

@@

\begin{rmk}
For those coming from an operadic background, it may be helpful to recognize that our approach is a variant of a familiar convolution construction.
The functor $\bU_n \fh = \cliels(\Omega^*_c \otimes \fh)$ determines an algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$,
while the functor $\cliels(\Omega^* \otimes \fg)$ determines a {\em co}\/algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
The algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ assigns the graded vector space
\[
\Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg), \cliels(\Omega^*_c(V) \otimes \fh))
\] 
to each open set $V$,
twining together this coalgebra and algebra.
\owen{This has a name, but I'm blanking at the moment.}
The differential can be seen as a twisting cocycle arising from a choice of map $f$;
there is a natural basepoint to the space of differentials on this graded vector space by taking the usual differential of a hom-complex.
\end{rmk}

%
%\def\conv{{\rm Conv}}
%
%\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
%
%\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^! \to A$ from $C^! = \conv(C,1)$, the ``Koszul dual'' $\cO$-algebra to the coalgebra $C$. This cocycle can be used to twist the differential of $\conv(C,A)$. Hopefully this admits an obvious deformation-theoretic interpretation.}
%
%\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}

@@

Our goal in this subsection is to construct a map of factorization algebras
\[
\ev_{{\bf f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
\]
while in the next subsection we will show it fits into a centralizer diagram.
To produce our map, we first construct it separately on each open subset and then explain why the construction is functorial.

Let $V \subset \RR^n$ be open.
The canonical pairing between Lie algebra chains and cochains provides a canonical cochain map
\[
\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \cliels(\Omega^*(V) \otimes \fg) \to \cliels(\Omega^*_c(V) \otimes \fh)_f.
\]
The canonical inclusion $\Omega^*_c(V) \otimes \fg \hookrightarrow \Omega^*(V) \otimes \fg$ induces a canonical inclusion 
\[
\cliels(\Omega^*_c(V) \otimes \fg) \hookrightarrow \cliels(\Omega^*(V) \otimes \fg)
\]
and hence, precomposing this inclusion with the pairing, we obtain our desired map
\[
\ev_{{\bf f}}(V): \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
\]
for each open~$V$.

@@

\begin{lmm}
The assignment
\[
V \mapsto \ev_{{\bf f}}(V)
\]
determines a natural transformation between functors from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
\end{lmm}

@@

%\greg{
%We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.\\
%First note that compactly supported form embeds in all forms, therefore we can apply 
%any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
%to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
%\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
%\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
%  \\
% (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
%\end{equation} induced by this embedding  in all forms followed by evaluating on a function.\\
%Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
%$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
%We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
%\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
%B(\emptyset) \ar[r] & B(U)  } 
% \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
% $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
% of the factorization structure of 
% the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
% The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
% \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
% $B$. We therefore obtain a canonical splitting of factorization algebras 
% \begin{equation}\label{eq:splittingbyaugm}
%   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
% \end{equation}
%given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
%a natural grading on it.\\
%We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
%\begin{multline}\label{eq:defevforconnected}
% \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
% \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
% \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
% \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
% \right) \\
% \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
% B(W)
%\end{multline}
%where $\mathbf{f}$ is the factorization algebra morphism  we are given.
%In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
%we have 
%\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
%We extend this construction  to any 
% open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
% More precisely, 
%  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
%of its connected components. Using, the natural isomorphisms of complexes 
%\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
%\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
%\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
%\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
%$\bigotimes_{i\in I} B(U_i) 
%\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
% (natural) decomposition 
%\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
% \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
% \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
% \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
%\end{multline}
%and we can therefore define 
%\begin{multline}\label{eq:defineevf}
% \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
% \\ \stackrel{\simeq}\longrightarrow  
%\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
% \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
% \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
% \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
%\end{multline}
%where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
%and~\eqref{eq:defevforconnected}.
%\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
%things to do (like completion) for non-finitely dimensional Lie algebras}
%\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
%out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}\\
%\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
%the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
